\documentclass[12pt,a4paper,oneside,notitlepage]{report}
\usepackage[a4paper]{geometry}

% -------------------------------------------------
% None of these packages are required by ecochapter
\usepackage{verbatim}
\usepackage{color}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage[T1]{fontenc}
\usepackage{lmodern} %font
% -------------------------------------------------

\usepackage{ecochapter}

\begin{document}

\echapter*{Comparison Notes}
\verb|ecochapter| was created mainly as a better way of sectioning a formal report, without wasting space or labelling such as "Chapter 1 \textbackslash <Title>" where "1 <Title>" is more appropriate.

I have included a page of the headings as displayed using the \verb|ecochapter| package, followed by the same examples using the standard \LaTeX commands.

The [Compare] hyperlinks reference the heading of the opposite type (\verb|ecochapter| links to \LaTeX and vice versa).

\emph{As a side effect you will see that }\verb|ecochapter|\emph{ headings work better with }\verb|hyperref|\emph{ than their \LaTeX counterparts.}

\newpage
\chapter{chapter --- new page \hyperref[echapter]{Compare}}\label{chapter}
Text after chapter. {\color{blue} Note that the original \verb|\chapter| forces a new page. There is also lots of space above the heading.

I have numbered the first chapters to show the difference in styling. The method here undoubtedly looks good, but is not always appropriate.}

\chapter*{chapter --- after text \hyperref[echapterplus]{Compare}}\label{chapterplus}
\section*{section --- after chapter \hyperref[esectionplus]{Compare}}\label{sectionplus}
Text after section. {\color{blue} \verb|\chapter| immediately followed by \verb|\section| wastes vertical space between headings.}

\section*{section --- after text \hyperref[esection]{Compare}}\label{section}
\subsection*{subsection --- after section \hyperref[esubplus]{Compare}}\label{subplus}
Text after subsection.

\subsection*{subsection --- after text \hyperref[esubs]{Compare}}\label{sub}
\subsubsection*{subsubsection --- after subsection \hyperref[esubsubplus]{Compare}}\label{subsubplus}
Text after subsubsection

\subsubsection*{subsubsection --- after text \hyperref[esubsub]{Compare}}\label{subsub}

\echapter{echapter --- new page \hyperref[chapter]{Compare}}\label{echapter}
Text after chapter.

\echapter*+{echapter --- after text \hyperref[chapterplus]{Compare}}\label{echapterplus}
\esection*+{esection --- after chapter \hyperref[sectionplus]{Compare}}\label{esectionplus}
Text after section. {\color{blue} Using \verb|\esection+| immediately after \verb|\echapter| collapses space between headings. The "\verb|+|" modifier does the same for all commands. The exception is that \verb|\echapter+| prevents a new page for the chapter.}

\esection*{esection --- after text \hyperref[section]{Compare}}\label{esection}
\esubsection*+{esubsection --- after section \hyperref[subplus]{Compare}}\label{esubplus}
Text after subsection.

\esubsection*{esubsection --- after text \hyperref[sub]{Compare}}\label{esub}
\esubsubsection*+{esubsubsection --- after subsection \hyperref[subsubplus]{Compare}}\label{esubsubplus}
Text after subsubsection

\esubsubsection*{esubsubsection --- after text \hyperref[subsub]{Compare}}\label{esubsub}

\eappendix{Extra stuff}
\eappendix+{Extra stuff samepage}
\end{document}